\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer} % Job title
    {Uber} % Organization
    {San Francisco, CA} % Location
    {October 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, implemented, and maintained an \textbf{MVCS Java service} to deliver 100s of Uber-provisioned cloud hosts in minutes.}
        \item {Collaborated on a proof-of-concept cloud datacenter, and performed an experiment to estimate the viability of migrating \textbf{over 3000} services to new Uber datacenters.}
        \item {Created \textbf{Uber's first production cloud datacenter} using our automation, drove policy and projects around it, and acted as the primary owner.}
        \item {Lead the migration of \textbf{70,000} service-cores from a legacy on-premises datacenter to the new cloud datacenter.}
        \item {Designed and lead implementation of Uber's \textbf{cloud IaaS platform}, composed of goalstate-driven Go microservices.}
        \item {Represented my team in \textbf{cross-org collaborations} to create Uber's next-gen foundational infrastructure.}
        \item {Co-founded an \textbf{internal resource group} for supporting gender minorities in infrastructure roles.}
      \end{cvitems}
    }
    
  \cventry
    {Security Engineering Intern} % Job title
    {Security Innovations} % Organization
    {Seattle, WA} % Location
    {June 2015 - September 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed \textbf{black-box and white-box penetration testing} engagements with 4 clients on their in-production and unreleased products, using industry best-practice threat analysis, test planning, and vulnerability reporting. These products varied from physical devices to web applications.}
        \item {Researched the current academic and industry climate on \textbf{GPS spoofing}, and wrote a long-form presentation with accompanying short whitepaper.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Epic Systems} % Organization
    {Madison, WI} % Location
    {June 2014 - September 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Added a feature to EpicCare Inpatient 2015 that creates a \textbf{seamless user interface} with third-party hardware using an in-house RESTful API queried by VisualBasic and presented with HTML/CSS/VBScript.}
      \end{cvitems}
    }

\end{cventries}
